---
title: "Custom Set 01"
author: "Xinqian Cai"
date: "2021/9/11"
output: html_document
---

## Practice
```{r}
library(tidyverse)
```
```{r}
deck <- tibble(
  # tibble is a more flexible data.frame
  card = rep(
    c("ace",
      "deuce",
      "three",
      "four",
      "five",
      "six",
      "seven",
      "eight",
      "nine",
      "ten",
      "jack",
      "queen",
      "king"
    ),4),
  suit =
    rep(c(
      "diamonds", 
      "hearts", 
      "clubs", 
      "spades"),
        each = 13),
  color = rep(c("red", 
                "black"),
              each = 26)
)

glimpse(deck)
```

## Question 1
```{r}
pr_black <- deck |>
  filter(color == "black") |>
  nrow()/nrow(deck)

pr_red <- deck |>
  filter(color == "red") |>
  nrow()/nrow(deck)

pr_red * pr_black
```
```{r}
pr_king <- deck |>
  filter(card == "king") |>
  nrow()/nrow(deck)

pr_ace <- deck |>
  filter(card == "ace") |>
  nrow()/nrow(deck)

pr_king_and_ace <- deck |>
  filter(card == "king" & card == "ace") |>
  nrow()/nrow(deck)

pr_king + pr_ace - pr_king_and_ace
```
```{r}
pr_ace1 <- deck |>
  filter(card == "ace") |>
  nrow()/nrow(deck)

pr_ace1 * pr_ace1
```

## Question 2
```{r}
Hands <- sample_n(deck, 5)

View(Hands)
```
```{r}
n <- 52; k <- 5

Num_hands <- choose(n,k)

Num_hands
```
There are 2598960 kinds of different hands.

## Question 3 
```{r}
totalhands <- sum(choose(52,5))

number_2samesuits_3diffsuits <- choose(13,2) * 13^3 * 4

pr_number_2samesuits_3diffsuits <- number_2samesuits_3diffsuits / totalhands

pr_number_2samesuits_3diffsuits
```

## Question 4
```{r}

zero_ace <- choose(39,5)  # Choosing 5 cards from the cards set that without ace

pr_atleast_oneace <- (choose(52,5) - zero_ace) / choose(52,5)

pr_atleast_oneace
```
## Question 5
```{r}
choose(6,2) # Choosing 2 persons from 6 employees as a two-member committee, counting the number of ways that can form a two member committee.
```
```{r}
num_pre_vice <- choose(6,2) * factorial(2)  # choosing 2 persons from 6 employees as a two-member committee, counting the number of ways that can form a two member committee; order matters which means eg. (a,b) is not equal to (b,a) ; multiple the repeated ones with different order.

num_pre_vice
```
## Question 7
```{r}

fairdie <- replicate(1000,sample(1:6, 3, replace = TRUE))

```

```{r}
loaded_die_6 <- replicate(1000,sample(1:6, replace = TRUE, prob = c(1/6, 1/6, 1/6, 1/6, 1/6, 1/2) ))
```


```{r}
loaded_die_5_6 <- replicate(1000,sample(1:6, replace = TRUE, prob = c(1/6, 1/6, 1/6, 1/6, 1/3, 1/3) ))
```

## Hi Nico! I am sorry that I does not make a plot because I do not know how to output the sampling I have done as a tabble that allows me to draw a plot and calculate the mean though I have looked for the solutions online for almost 3 hours. Would you mind talking more about this quesiont?



